---
title: "Getting started with the Binomial Package"
author: "Melissa Ly"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to the Binomial Package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
  \usepackage[utf8]{inputenc}
---
```{r setup}
devtools::document() 
library(binomial)
```

```{r echo = FALSE, message= FALSE}
knitr::opts_chunk$set(collapse = T, comment="#>")
library(binomial)
library(ggplot2)
```

## About the Binomial Distribution
The Binomial distribution is perhaps the most famous probability distribution among discrete
random variables. This is the theoretical probability model that we use when calculating
probabilities about the number of successes in a fixed number of random trials performed
under identical conditions (assuming a constant probability of success on each trial).

## An Example

A classic example of a binomial random variable X involves the number of Heads (or Tails)
that you get when tossing a coin n ≥ 0 times. Say you are interested in finding the number of ways you could get 2 heads in 10 coin flips.
```{r}
bin_choose(n=10, k=2)
```
This function will calculates the number of combinations in which k successes can occur in n trials

## Probablity of Success

Say you are interested in finding the probability of getting three heads in four tosses of a fair coin: P(X = 3 heads in 4 tosses). To find the answer, we use the function for the binomial probability:
```{r}
bin_probability(success = 3, trials = 4, prob = 0.5)
```


## Views
See a table of all the probabilities of success given the corresponding trials

```{r}
bin_distribution(trials = 5, prob = 0.5)
```


## Visualize Success

Visualize your probablity of success through a bar plot!

Plot a line graph of the table derived.
```{r}
plot(bin_distribution(trials = 5, prob = 0.5))
```


## Get Random!

Create a binomial random variable givent the number of trials and chance of heads and find its summary statistics of the random variable
```{r}
bin_var <- bin_variable(trials=5, prob=0.5)
bin_var

summary(bin_var)
```

## Summary Statistics

Calculate various individual statistics 

```{r}
bin_mean(5, 0.5)
bin_variance(5, 0.5)
bin_mode(5, 0.5)
bin_skewness(5, 0.5)
bin_kurtosis(5, 0.5)
```

And the outputs are the exact same as our previous calculations! These functions are extemely useful and help us compute crunch meaningful data so thanks for using this package!
